STAT 450 Project: Real Estate

### 2020-03-05 doc/RealEstate_Yuting_Wen.Rmd

Our client is a real estate data analyst in Metro Vancouver who analyzes the market trend to make a market prediction for his company and future client. He is interested in a good prediction model that can accurately predict future mill rates, given the past data like the past mill rates and the past assessment values, in Metro Vancouver. Data cleaning, exploratory data analysis, and linear models with different kinds of regulazations were used to analyze the relationship between mill rate and other factors and predict future mill rates. Data cleaning is performed to aggregate our data into summary statistics and also reduce the number of data entries. Exploratory analysis has shown that there is a strong correlation between mill rate and municipal budget and strong correlation between mill rate and assessment in some municipalities. The results of exploratory analysis have also shown that there is no clear difference among full linear Regression model with all features (Year, TaxClassCode, Municipalities, assessTotal_pct, tax (budget), landTotal, improvementTotal, numProperties) and reduced linear regression models (Ridge, Lasso and Elastic net).

@@

A full linear model with all features, a few reduced linear models with regularzations like the LASSO, Ridge Regression are used to train our predictive model. Once we have finished fitting those models, we will use the mean squared training error to evaluate the performance of our model.

@@

We also made scatterplot of mill rate vs. assessment, mil rate vs. municipal budget, mill rate vs. landTotal (total land assessment value), mill rate vs. improvementTotal (total improvement assessment value), and mill rate vs. numOfProperties (number of properties) to see the correlation between each of the two factors. ANOVA analysis was also performed to see the correlations between mill rate vs. tax class, mill rate vs. year and mill rate vs. municipality.

@@

>>>>

Our client is a real estate data analyst in Metro Vancouver who analyzes the market trend to make a market prediction for his company and future client. He is interested in a good prediction model that can accurately predict future mill rates, given the past data like the past mill rates and the past assessment values, in Metro Vancouver. Data cleaning, exploratory data analysis, and linear models with different kinds of regularzations were used to analyze the relationship between mill rate and other factors and predict future mill rates. Data cleaning is performed to aggregate our data into summary statistics and also reduce the number of data entries. Exploratory analysis has shown that there is a strong correlation between mill rate and municipal budget and between mill rate and assessment in some municipalities. The results of exploratory analysis have also shown that there is no clear difference among full linear Regression model with all features (year, tax class code, municipality, total Assessment value, tax (budget), total land assessment value, total improvement assessment value, number of properties) and reduced linear regression models (Ridge, Lasso and Elastic net), while they still have relatively low error.

@@

A full linear model with all features, a few reduced linear models with regularzations like the LASSO, Ridge Regression are used to train our predictive model. Once we have finished fitting those models, we will use the mean squared test error to evaluate the performance of our model.

@@

We also made scatterplot of mill rate vs. assessment, mil rate vs. municipal budget, mill rate vs. total land assessment value, mill rate vs. total improvement assessment value, and mill rate vs. number of properties to see the correlation between each of the two factors. ANOVA analysis was also performed to see the correlations between mill rate vs. tax class, mill rate vs. year and mill rate vs. municipality.

@@

We used R package called "ggplot" to visualize our results.
